The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-04 paper.tex
update

To this end, this work introduces a dense thin disc of interstellar medium\
around a jet source to deflects and decelerates the jets,\
in an attempt to remedy the symmetry problem of the Galactic bubbles.\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
           Note that the left panel is the\
           photon flux of the diffuse component reconstructed by the D$^3$PO\
           algorithm \citep{Selig2015} that analyzes\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
           and removes the contribution from point-like component.
  }
  \label{fig__gammaRay}
\end{figure*}

>>>>

To this end, this work introduces a dense thin disc of interstellar medium\
around a jet source to deflects and decelerates the inclined jets,\
in an attempt to remedy the symmetry problem of the Galactic bubbles.\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux\
           in the energy bin $76.8-153.6$ GeV.\
           Note that the left panel is the\
           photon flux of the diffuse component reconstructed by the D$^3$PO\
           algorithm \citep{Selig2015} that analyzes\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
           and removes the contribution from point-like component.
           The red arrow at the center of the\
           top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
           to the disc normal in 1.2 Myr.]
  }
  \label{fig__gammaRay}
\end{figure*}
